An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials

### 2020-05-13 gas-adsorption/gas-ads-body.tex
fixed the conclusion.

The second limitation of our proof arises in the assumption of a rigid substrate. The rigid substrate acts as a static potential energy field for gas molecules that is unchanged by the adsorption of gas.
% The second limitation of our proof arises in the assumption of a rigid substrate, which acts as a static potential energy field for gas molecules that is unchanged by the adsorption of gas.
For most porous materials this is a reasonable approximation, and this assumption is frequently made in both the simulation and theory of porous materials~\cite{witman2017influence}. However, there are cases where the substrate can in effect provide a very strongly gas-density-dependent interaction through structural flexibility~\cite{schneemann2014flexible}. A flagship example is MOF Co(bdp)~\cite{choi2008broadly}, which possesses a wine-rack-like topology capable of hinge motion. At low methane pressure, Co(bdp) adopts a collapsed, nonporous state, but expands to a porous state and fills with gas at higher pressures~\cite{mason2015methane}. This allows Co(bdp) to fully expel its residual gas at low pressures.
Our upper bound does not consider such material effects and thus flexible materials could have significantly higher deliverable capacities.
% Such materials can indeed violate our upper bound and thus could lead to significantly improved deliverable capacities.

>>>>

The second limitation of our proof arises in the assumption of a rigid
substrate. The rigid substrate acts as a static potential energy field for gas
molecules that is unchanged by the adsorption of gas. For most porous materials
this is a reasonable approximation, and this assumption is frequently made in
both the simulation and theory of porous materials~\cite{witman2017influence}.
However, there are cases where the substrate can provide a very strong
gas-density-dependent interaction through structural
flexibility~\cite{schneemann2014flexible}. A flagship example is MOF
Co(bdp)~\cite{choi2008broadly}, which possesses a wine-rack-like topology
capable of hinge motion. At low methane pressure, Co(bdp) adopts a collapsed,
nonporous state, but expands to a porous state and fills with gas at higher
pressures~\cite{mason2015methane}. This allows Co(bdp) to fully expel its
residual gas at low pressures. Our upper bound does not consider such material
effects, and thus flexible materials could have significantly higher
deliverable capacities.
